\documentclass[11pt]{article}

\title{Dungeon Runner, team 4}
\author{Jordan Lynn, Chase Guyer, Madeleine Brennan}

\begin{document}

    \maketitle

    \section{Goals}
    The overreaching goal for the player is to defeat the final boss on the lowest floor of the game. Throughout the levels there will be smaller sub-goals that must be achomplished to win in no particular order they are.
        \subsection{Level Boss}
            Every fifth level a power boss will spawn, the user must defeat this boss to continue onto the lower levels. This boss will also drop an evevator key which will enable the player to quickly go back up and down floors to which he/she has a elevator key to.
    
    \section{Backstory}
    This game takes place in the game software development company Cyber Inc. Founded by current company CEO C.J. Free, it has quickly made its way into the headlines with its top of the line games. What the public or lower company members do not know is that the game development and sales is just a cover up for the CEO's intentions. Originally from the planent Gamma, Mr. Free and the board of directors are creating a device that will link human brains together for a limitless, reusable processor for computer computations. Hidden underneath Cyber Inc is a maze-like series of levels where the aliens working under Cybermind, aka C.J. Free, are building this device in depths far enough that no known frequencies could disturb it. 

    \section{Story Line}
    Players enter the story as a software developer at Cyber Inc. There are two possible ways that the player become aware to the hidden intentions of the company. One is during the annual company system backup a mysterious file appears on the players computer, containing mysterious code in an unknown language as well as a floorplan of Cyber Inc, showing a room that the player did not know of before. After this the player's character finds the entrance to this room, starting gameplay. The other way to start the game is the player character falls asleep at their cubical and wakes up hearing talking after everyone else comes home. Looking over the cubical wall they see Mr. Free talking to their manager, before disappearing through a door they've never noticed before. Once the coast is clear the player sneaks through the door out of curiousity, starting gameplay.
        \subsection{Game Play Story Line}
            Gameplay begins as the player explores behind the unknown door in Cyber Inc, which locks after they enter. Behind this door is a large room very similar to that they just left, but is filled with members of the development team that have been brainwashed to work for the aliens, and these team members notice that player/s do not belong in that area and will confront/attack upon contact. This forces the player to adapt and find/create weapons from office supplies in order to find a way out of the room, which is an elevator that leads them deeper into the operation. As the player/s move deeper and deeper into the coorperations levels, they begin to notice that things begin to become less mundane and more alien, as do the enemies. In the final few levels everything is completely alien, and the final level the player/s face off against Cybermind. 
        
    

    \section{}

    \section{User Interface}
        The user interface Is composed of three main components; The game map, the status bar, and the player management pane.
	The game window is composed of the game map taking the leftmost 80\% of the screen, the management pane taking the remaining 20\%, and the status bar will be centered on the bottom of game map screen.

	\subsection{Map \& Viewpoint}
	The game will use a 2D, Top-Down perspective with the camera looking at a slight angle from vertical; For example, the front and top of a box on the ground are visible, but not the sides, back, and bottom.
	The ``far'' walls (those away from the camera, facing towards the bottom of the screen) are visible, the ``near'' walls (near the bottom of the screen facing up) will not be visible.

	\subsection{Combat and Status bar}

	Combat actions, skills, and player status will be displayed at the bottom of the game window, overlaying the game map. It will be composed of a player information box, skills selector, and item selector.
	The player information box contains critical stats like health and synergy points overlayed with a portrait view of the player that visually depicts status and debufs  (similar to ``Doom'').
	The skills and items selectors will be a series of boxes containing icons representing unlocked skills and docked items that the player can click to activate.

	\subsection{Player Management Pane}
	The Inventory, Skills \& Stats, Minimap, Equipped items, and Objectives will be displayed one at a time on slides within the Player Management pane.
	A series of tabs with representative icons will line the top of the Pane so that the player can switch between slides while playing.

	\subsection{Player Controls}
	The player controls his avatar with either the arrow keys of his/her keyboard or the mouse. Left clicking a location will cause the avatar to path-find to that location.
	Right clicking an object will cause the avatar to attempt to interact with that object (use/open/attack) and move there if necessary.
	If using the keyboard, running into a solid object will attempt to interact with that object.

\end{document}
